\documentclass[12pt]{article}
\usepackage[top=1.5cm, bottom=1cm, left=1in, right=1in]{geometry}
\usepackage{fancyhdr}

\setlength{\parskip}{0.5em}

\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
% \fancyfoot[L]{\textit{Séon O'Shannon} - \textit{Diversity Statement}}
% \fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt} % Remove the top line

\begin{document}

\begin{center}
    \Large{\textbf{Diversity Statement for Séon O'Shannon}} \\
    University of Colorado Boulder - Biochemistry Ph.D.
\end{center}

\vspace{0.1cm}

The hallmark of prion disease is a short feedback loop between an organism and itself. Thus a healthy system is necessarily born of a large and varied sampling of the environment within which the system is enmeshed. I believe this holds true for animals, people, communities, and most abstracted, complex systems.

Regardless of whether it's a small ensemble playing music, a business meeting the needs of its customers, or a university lab doing cutting edge research, a variegated perspective benefits all and yields more robust results. Across the CU Boulder campus, I will do my absolute best to engender an environment of communal ownership, supportive enablement, and growth.

It is my goal to build strong connections, communities, and systems. I grew up without a father and with a mentally ill, single mother. As a child, my home was a small trailer with a leaky roof, cramped with papers and other "important" items. I took the bus home from elementary school, cooked myself top ramen, and spent my evenings walking along the beach, watching the sunset. Despite being poor, I was still given ample opportunities to succeed. While attending high school in Nevada, I became an Eagle Scout, engaged in and led regular community service, participated in the Amateur Radio Emergency Services, played bassoon in the Reno Philharmonic Youth Orchestra and the Reno Video Game Symphony, took 11 AP classes, taught myself C++, and, in my senior year, took college biology.

I would not have been able to accomplish so much if not for the generosity and assistance my community lent me. In turn, I strive to give back and help others achieve their dreams even if they began their lives with few advantages. I've had friends through the years, grad students included, who have not received the support they've needed. Some of those have, unfortunately, committed suicide. As friends, colleagues, and leaders, mental health is not something we can afford to ignore. Given this, I always make sure to check in with those around me and help them feel seen and appreciated.

In my professional role as a senior software engineer for Zywave, I was privileged to work on a team of diverse individuals which is rare in the software field. I believe the success our team experienced was largely due to our heterogeneity. For example, our platform handled billions of dollars in insurance quotes a month and experienced virtually 0% downtime. While at Zywave, I prioritized investing in others' growth. I mentored and funded colleagues in my community, empowering them to build open-source software and time-saving tools that are still in use today.

Being inclusive of those with disabilities can improve team performance as much as gender and cultural diversity. I now provide accessibility-driven technology enablement services for science communication and outreach organizations across the nation. Groups like the Great Basin Native Plant Project, Great Plains Fire Science Exchange, Pacific Climate Exchange, and the Indigenous Environmental Network all look to me for guidance and support on how to structure their information so that it's available to as wide an audience as possible. As these groups came to embrace technological accessibility, the quality of their digital assets improved dramatically. For example, some clients have engaged my company to remake their PDFs as web pages that can be read with screen readers; the new pages were so much better that we were asked to convert them into new PDFs for print.

I firmly believe in providing equitable opportunities and will do what I can to enable underrepresented peoples on campus. It would be my pleasure to uplift the community and encourage the spirit of inclusion and collaborative success at the University of Colorado Boulder.

\end{document}